Draft Figures: 12.23.18

### 2019-01-04 draft_figures_12.23.18.Rmd
updated 2016_projection_updated to only include data instead of projections

@@

ggplot(data = fisheries_KOBE_ram, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot: RAM only Fisheries")

>>>>

a = fisheries_recent %>% 
  filter(Dbase == "RAM") %>% 
  ggplot(aes(BvBmsy, FvFmsy, color =Dbase )) + 
  geom_point() + 
  coord_cartesian(xlim = c(0,4), ylim = c(0,4))

timeseries_values_views %>% 
  filter(year == 2016) %>% 
  select(BdivBmsypref,UdivUmsypref) %>% 
  na.omit() %>% 
  nrow()
  ggplot(aes(BdivBmsypref,UdivUmsypref)) + 
  geom_point()

  a
```

@@

s
```
